Supporting Information:\\Black-swan events in animal populations

### 2016-11-10 text/supp.tex
Reorder supplementary figures

To test if the prior on \(\nu\) influenced our estimate of black-swan dynamics,
we refit our models with weaker and stronger priors. Our base model used a
prior on \(\nu\) of Truncated-Exponential(0.01, min.\ = 2). For a weaker prior
we used Truncated-Exponential(0.005, min.\ = 2) and for a stronger prior we
used Truncated-Exponential(0.02, min.\ = 2) (Fig.~\ref{fig:priors}C). Note that
the base and weaker priors are relatively flat within the region of \(\nu <
20\), which is the region we are concerned about when categorizing
populations as heavy tailed. We also considered using a Uniform(\(0, 1\))
prior on \(1/\nu\) as used in \citet{gelman2014}, but this
prior puts considerably more weight on lower (heavy-tailed) values of \(\nu\)
than the truncated exponential priors considered here,
and the results are therefore not shown.

>>>>

To test if the prior on \(\nu\) influenced our estimate of black-swan dynamics,
we refit our models with weaker and stronger priors. Our base model used a
prior on \(\nu\) of Truncated-Exponential(0.01, min.\ = 2). For a weaker prior
we used Truncated-Exponential(0.005, min.\ = 2) and for a stronger prior we
used Truncated-Exponential(0.02, min.\ = 2) (Fig.~\ref{fig:priors}C). Note that
the base and weaker priors are relatively flat within the region of \(\nu <
20\), which is the region we are concerned about when categorizing
populations as heavy tailed. We considered using a Uniform(\(0, 1\))
prior on \(1/\nu\) as used in \citet{gelman2014}, but this
prior puts considerably more weight on lower (heavy-tailed) values of \(\nu\)
than the truncated exponential priors considered here,
and the results are therefore not shown.
Furthermore, we considered the prior suggested in \citet{juarez2010} of
$\nu \sim \mathrm{Gamma}(2, 0.1)$, again limited to $\nu > 2$.
Compared to our main truncated exponential prior,
this prior places a higher probability density at $\nu < 10$ ($0.25$ vs.\ $0.08$)
and has a mode at $\nu = 10$.
This prior raised the estimated value of $\nu$
for some of the populations identified as heavy-tailed
with our default prior,
but overall gave us similar inference
with a Spearman correlation of 0.90 between Pr($\nu < 10$)
for the two priors.
